DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-02-01 paper/related.tex
related and future

These reseach efforts are expected to make complex DNNs more
accessible for real-time embedded systems.

>>>>

These research efforts are expected to make complex DNNs more
accessible for real-time embedded systems. We plan to investigate the
feasibility of these approaches in the context of DeepPicar so that we
can use even more resource constrained micro-controller class
computing platforms instead of Raspberry Pi3.
